### 2011-05-10 paper.tex

Thus, in order to prove Theorem \ref{amplify}, we just need to show that any \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class is closed under majority reductions. In order to show that these are closed under majority reductions, we will need the help of another property:
\begin{definition}\label{defintersection}\emph{
We say that a class $C$ is \emph{closed under intersection} if for any language $L \in C$, the language $\intersection(L) = \{(x_1,...,x_k) : k\in\mathbb{N}, x_i \in L_i ~ \forall i\}$ is in $C$.
}\end{definition}
We will demonstrate that all $\{\Sigma, \Pi, \bp, \parity\}$-constructible complexity classes are closed under intersection and under majority reductions. To do this, we will use induction on the number of operators in $C$. Clearly $\p$ is closed under intersection and majority reductions. Thus, the result follows from the following two lemmas:

>>>>

Thus, in order to prove Theorem \ref{amplify}, we just need to show that any \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class is closed under majority reductions. In order to show that these are closed under majority reductions, we will need the help of another property:
\begin{definition}\label{defintersection}
We say that a class $C$ is \emph{closed under intersection} if for any language $L \in C$, the language $\intersection(L) = \{(x_1,...,x_k) : k\in\mathbb{N}, x_i \in L_i ~ \forall i\}$ is in $C$.
\end{definition}
We will demonstrate that all $\{\Sigma, \Pi, \bp, \parity\}$-constructible complexity classes are closed under intersection and under majority reductions. To do this, we will use induction on the number of operators in $C$. Clearly $\p$ is closed under intersection and majority reductions. Thus, the result follows from the following two lemmas:
